Mixed effect tweedie model in TMB

### 2019-04-05 analysis/tmb-sensor-explore/2-fit-temperature.Rmd
Identify stage in code where predict error is occuring

```{r}
library(tidyverse)
library(sdmTMB)

@@

set.seed(39201114)
withheld_fe <- sample(d_trawl$fishing_event_id, size = round(nrow(d_trawl) * .2))
d_withheld <- filter(d_trawl, fishing_event_id %in% withheld_fe)
d_fit <- filter(d_trawl, !fishing_event_id %in% withheld_fe)
nrow(d_fit)
nrow(d_withheld)
unique(d_withheld$year)
unique(d_fit$year)

# FIXME: need to work out a bug in production on this new data set
# It's crashing TMB.
d_fit <- d_trawl
d_withheld <- d_trawl
spde <- make_spde(d_fit$X, d_fit$Y, n_knots = 250)
plot_spde(spde)

m_temp1 <- sdmTMB(d_fit, temperature_c ~ 0 + as.factor(year) + depth_scaled,
  # time_varying =  ~ depth_scaled + depth_scaled2,
  time = "year", spde = spde, family = gaussian(link = "identity"), ar1_fields = FALSE,
  anisotropy = FALSE, include_spatial = TRUE, silent = TRUE)

m_temp1$model$par

# 2 * plogis(m_temp1$model$par[["ar1_phi"]]) - 1
exp(m_temp1$model$par[["ln_phi"]])

predictions <- predict(m_temp1)
predictions$data$residuals <- residuals(m_temp1)

plot_map <- function(dat, column = "est") {
  ggplot(dat, aes_string("X", "Y", colour = column)) +
    geom_point() +
    facet_wrap(~year) +
    coord_fixed()
}

plot_map(predictions$data, "est") +
  scale_colour_viridis_c() +
  ggtitle("Prediction (fixed effects + all random effects)")

plot_map(predictions$data, "est_fe") +
  ggtitle("Prediction (fixed effects only)") +
  scale_colour_viridis_c()

>>>>

```{r setup}
library(tidyverse)
library(sdmTMB)

@@

set.seed(39201114)
```

```{r}
withheld_fe <- sample(d_trawl$fishing_event_id, size = round(nrow(d_trawl)*.2))

d_withheld <- filter(d_trawl, fishing_event_id %in% withheld_fe)

d_fit <- filter(d_trawl, !fishing_event_id %in% withheld_fe)

nrow(d_fit) # 3774
nrow(d_withheld) # 943
unique(d_withheld$year) 
unique(d_fit$year)
length(unique(d_fit$year))

# FIXME: need to work out a bug in production on this new data set
# It's crashing TMB.

#d_fit <- d_trawl
#d_withheld <- d_trawl
```

```{r}
spde <- make_spde(d_fit$X, d_fit$Y, n_knots = 250)
plot_spde(spde)
```

```{r}
m_temp1 <- sdmTMB(d_fit, temperature_c ~ 0 + as.factor(year) + depth_scaled,
  # time_varying =  ~ depth_scaled + depth_scaled2,
  time = "year", spde = spde, family = gaussian(link = "identity"), 
  ar1_fields = FALSE,
  anisotropy = FALSE, 
  include_spatial = TRUE, 
  silent = FALSE)

```

```{r}
m_temp1$model$par
# 2 * plogis(m_temp1$model$par[["ar1_phi"]]) - 1
exp(m_temp1$model$par[["ln_phi"]])
```

```{r}
# FIXME: Error in `$<-.data.frame`(`*tmp*`, "est", value = c(7.12313541783276, :replacement has 4716 rows, data has 4717
predictions <- predict(m_temp1)

attributes(m_temp1)

# find source of error in predict function
object <- m_temp1

 nd <- object$data # this has 3,774 rows of data
 lp <- object$tmb_obj$env$last.par # this has 6583 length(lp)
  r <- object$tmb_obj$report(lp)
    length(r$omega_s) # 386
    length(r$epsilon_st) # this is 6176
    length(r$b_rw_t) # this has 16 time steps
    length(r$eta_i) # this is a vector of 3773

    nd$est <- r$eta_i # ERROR OCCURS HERE
    nd$est_fe <- r$eta_fixed_i # ERROR OCCURS HERE

attributes(r)

```

```{r}
predictions$data$residuals <- residuals(m_temp1)
```

```{r}
plot_map <- function(dat, column = "est") {
  ggplot(dat, aes_string("X", "Y", colour = column)) +
    geom_point() +
    facet_wrap(~year) +
    coord_fixed()
}
```

```{r}
plot_map(predictions$data, "est") +
  scale_colour_viridis_c() +
  ggtitle("Prediction (fixed effects + all random effects)")
```

```{r}
plot_map(predictions$data, "est_fe") +
  ggtitle("Prediction (fixed effects only)") +
  scale_colour_viridis_c()
